Score-based tests of measurement invariance: Use in practice

### 2013-08-30 frontiers/frontiers.Rnw
set up the full simulation 1 and simulation 2 in frontiers.Rnw file.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@247 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

## auxiliary code
source("simall.R")
source("mz.R")
source("../www/efpFunctional-cat.R")
source("../pkg/sctest.lavaan.R")

@@

\section{Simulation}
\section{Simulation 1}

 to which the proposed tests
are sensitive to the specific model parameter that violates measurement
invariance.  If, say, a factor loading violates measurement
invariance, it is plausible that this violation impacts other
parameters such as factor covariances or other loadings 
associated with the factor in question.  Thus, the goal of the
simulation was to examine the extent to which the proposed tests
attribute the measurement invariance violation to the parameters that
are truly in violation.

@@

\begin{figure}
\caption{Path diagram representing the factor analysis model 
         used for simulations.}
\label{fig:path}
\includegraphics{PathDiagram}
\end{figure}

@@

@@

>>>>

## auxiliary code
source("simall-ordinal.R")
source("mz.R")
source("../www/efpFunctional-cat.R")
source("../pkg/sctest.lavaan.R")
source("../www/mz-ordinal.R")
source("../www/estfun-lavaan.R")

@@

\section{Simulation}
\section{Simulation 1}
In Simulation 1, we examined the extent to which the proposed tests
are sensitive to the specific model parameter that violates measurement
invariance.  If, say, a factor loading violates measurement
invariance, it is plausible that this violation impacts other
parameters such as factor covariances or other loadings 
associated with the factor in question.  Thus, the goal of the
simulation was to examine the extent to which the proposed tests
attribute the measurement invariance violation to the parameters that
are truly in violation.

@@

@@

<<sim1>>=
## seed for replication
RNGkind(kind = "default", normal.kind = "default")
set.seed(1163)

if(file.exists("sim1.rda")) {
  load("sim1.rda")
} else {
  sim1 <- simulation(sim=c("sim1"), nobs=c(480),parms=c("loading","error","var"))
  sim1$nlevels <- factor(sim1$nlevels)
  levels(sim1$nlevels) <- paste("m=",levels(sim1$nlevels),sep="")
  sim1$nobs <- factor(sim1$nobs)
  levels(sim1$nobs) <- paste("n=",levels(sim1$nobs),sep="")
  levels(sim1$test) <- c("ordmax","ordwmax","catdiff")
  save(sim1, file="sim1.rda")
}
sim1$test <- factor(as.character(sim1$test),
  levels = c("ordmax","ordwmax","catdiff"),
  labels = c("ordmax","ordwmax","catdiff"))
@

@@

\section{Simulation 2}
In Simulation 2, we examine the extent to which the results of
Simulation 1 are robust to model misspecification. Specifically, we
generate data from the factor analysis model used in the previous
section, but with adding an extra loading from the second factor to the first
indicator (of the first factor).  The estimated model lacks this extra
loading, however. The goal of this simulation is to examine the proposed statitics'
power and spicificity under model misspecification.

\subsection{Method}
Measurement invariance violations could occur in
each of the three parameters from Simulation 1 (factor loading,factor covariance,unique
variance), and they could also occur in the extra,unmodeled loading. 
Sample size and magnitude of measurementinvariance violation were manipulated 
in the same way as they were in Simulation 1.The tested parameters are the same as Simulation
1,too.

<<sim2>>=
## seed for replication
RNGkind(kind = "default", normal.kind = "default")
set.seed(1163)

if(file.exists("sim2.rda")) {
  load("sim2.rda")
} else {
  sim2 <- simulation(sim=c("sim2"), nobs=c(480),parms=c("extra","extra+loading","extra+var","extra+error"))
  sim2$nlevels <- factor(sim2$nlevels)
  levels(sim2$nlevels) <- paste("m=",levels(sim2$nlevels),sep="")
  sim2$nobs <- factor(sim2$nobs)
  levels(sim2$nobs) <- paste("n=",levels(sim2$nobs),sep="")
  levels(sim2$test) <- c("ordmax","ordwmax","catdiff")
  save(sim2, file="sim2.rda")
}
sim2$test <- factor(as.character(sim2$test),
  levels = c("ordmax","ordwmax","catdiff"),
  labels = c("ordmax","ordwmax","catdiff"))
@
